---
title: "Preparing reference dataset: Swiss-SEP and Swiss addresses"
author: "Lorenz Leuenberger"
date: "`r date()`"
title-block-banner: "#e4003c"
format: 
  html:
    toc: true
    number-sections: true
    code-fold: false
    code-tools: true
    df-print: paged
    embed-resources: true
---


# Introduction

The Swiss neighbourhood index of socioeconomic position (Swiss-SEP) is an area-based measure of socioeconomic status for Switzerland. The Swiss-SEP was constructed by [Panczak et al.](https://doi.org/10.1136/jech-2011-200699) in 2012 and re-validated in [2023](https://doi.org/10.57187/smw.2023.40028). The Swiss-SEP used data from national census data and micro-censuses to assign a socioeconomic position to 1.54 million neighborhoods. The Swiss-SEP is a value between 0-100, where higher values relate to a higher socioeconomic position. Each Swiss-SEP value is linked to a geocode of an address (building) in Switzerland.

## Purpose

The purpose of this R script is to link the Swiss-SEP to all Swiss addresses, so that in a second step the clinical data warehouses (CDWs) of the SwissPedHealth project can search for patient addresses and get the linked Swiss-SEP value, see the html document named: "Transforming addresses to Swiss-SEP: Standard operating procedure". To link the Swiss-SEP to all Swiss addresses geocode information of addresses and Swiss-SEP are used.

This R script does not need to be run at the CDWs. The CDWs receive the reference dataset created with this script separately.

A dataset with all addresses in Switzerland and the corresponding geocodes of the building entrance is available from the [Federal Statistical Office (FSO)](https://www.housing-stat.ch/de/madd/public.html). For the last update in the SwissPedHealth project the building register (Gebäude und Wohnungsregister, GWR) was downloaded on 02.10.2025. The geocodes are given in the (CH1903+ / LV95 Swiss coordinate system)[https://www.swisstopo.admin.ch/de/wissen-fakten/geodaesie-vermessung/koordinaten/schweizer-koordinaten.html]. The Swiss-SEP dataset was provided by the Swiss National Cohort team at the Institute of Social and Preventive Medicine of the University of Bern, after signing a data sharing contract.

```{r}
#| warning: false

library(tidyverse)
library(here)
library(sf)
library(gtsummary)
library(readr)
library(data.table)
library(future.apply)


```

# Import and clean data

Import the Swiss-SEP dataset from the Swiss National Cohort:
```{r}
#| warning: false

swiss_sep <- read.csv(here("data","raw","ssep_open.csv"))

```

Clean the Swiss-SEP dataset:

```{r}
#| warning: false

swiss_sep <- swiss_sep %>%
  rename("geocode_E_sep" = "geox", "geocode_N_sep" = "geoy", "swiss_sep_1" = "ssep1", "swiss_sep_1_decile" = "ssep1_d", "swiss_sep_1_quintile" = "ssep1_q", "swiss_sep_1_tertile" = "ssep1_t", "swiss_sep_2" = "ssep2", "swiss_sep_2_decile" = "ssep2_d", "swiss_sep_2_quintile" = "ssep2_q", "swiss_sep_2_tertile" = "ssep2_t", "swiss_sep_3" = "ssep3", "swiss_sep_3_decile" = "ssep3_d", "swiss_sep_3_quintile" = "ssep3_q", "swiss_sep_3_tertile" = "ssep3_t",)

```


Import the addresses dataset from the FSO:

```{r}
#| warning: false

# ch
addresses <- read_tsv(here("data","raw","ch_02-10-2025","eingang_entree_entrata.csv"))
buildings <- read_tsv(here("data","raw","ch_02-10-2025","gebaeude_batiment_edificio.csv"))

```


Clean the datasets:

```{r}
#| warning: false

addresses <- addresses %>%
  select(EGID, STRNAME, STRNAMK, DEINR, DPLZ4, DPLZNAME, DKODE, DKODN, DOFFADR) %>%
  rename("street" = "STRNAME", "street_short" = "STRNAMK", "number" = "DEINR", "plz" = "DPLZ4", "city" = "DPLZNAME", "geocode_E_address" = "DKODE", "geocode_N_address" = "DKODN", "official_address" = "DOFFADR")


addresses[addresses == ""] <- NA

buildings <- buildings %>%
  select(EGID, GKODE, GKODN) %>%
  rename("geocode_E_building" = "GKODE", "geocode_N_building" = "GKODN")


buildings[buildings == ""] <- NA

```

Some of the building entrances do not have coordinates. Therefore, the building dataset is used to find the coordinates of the buildings for those addresses, instead of the entrance dataset.

```{r}
#| warning: false

addresses <- left_join(addresses, buildings, by = "EGID")

addresses <- addresses %>% 
  mutate(geocode_E_address = case_when(is.na(geocode_E_address)==TRUE ~ geocode_E_building,
                                       TRUE ~ geocode_E_address),
         geocode_N_address = case_when(is.na(geocode_N_address)==TRUE ~ geocode_N_building,
                                       TRUE ~ geocode_N_address))

missing_geo <- addresses %>% 
  filter((is.na(geocode_E_address)==TRUE | is.na(geocode_N_address)==TRUE))

```

23 addresses don't have coordinates for the entrance nor for the building.
Those addresses were searched and manually added from [map.geo.admin](https://map.geo.admin.ch/).

```{r}
#| warning: false

addresses <- addresses %>% 
  mutate(geocode_E_address = case_when(EGID == 192021721 ~ 2666314,
                                       EGID == 192032326 ~ 2705862,
                                       EGID == 192034223 ~ 2704159,
                                       EGID == 192037068 ~ 2699713,
                                       EGID == 192040785 ~ 2659330,
                                       EGID == 192041224 ~ 2645701,
                                       EGID == 192045031 ~ 2701782,
                                       EGID == 192045163 ~ 2649155,
                                       EGID == 192045180 ~ 2711737,
                                       EGID == 192045205 ~ 2668599,
                                       EGID == 192045230 ~ 2639526,
                                       EGID == 192045248 ~ 2575586,
                                       EGID == 192045254 ~ 2625845,
                                       EGID == 192045262 ~ 2591553,
                                       EGID == 192045347 ~ 2625845,
                                       EGID == 192045349 ~ 2639262,
                                       EGID == 192045371 ~ 2626471,
                                       EGID == 192045414 ~ 2646240,
                                       EGID == 192045417 ~ 2626609,
                                       EGID == 192045434 ~ 2597951,
                                       TRUE ~ geocode_E_address),
         geocode_N_address = case_when(EGID == 192021721 ~ 1267637,
                                       EGID == 192032326 ~ 1279102,
                                       EGID == 192034223 ~ 1237113,
                                       EGID == 192037068 ~ 1282350,
                                       EGID == 192040785 ~ 1245389,
                                       EGID == 192041224 ~ 1247200,
                                       EGID == 192045031 ~ 1232964,
                                       EGID == 192045163 ~ 1224396,
                                       EGID == 192045180 ~ 1236595,
                                       EGID == 192045205 ~ 1255637,
                                       EGID == 192045230 ~ 1236450,
                                       EGID == 192045248 ~ 1182666,
                                       EGID == 192045254 ~ 1266623,
                                       EGID == 192045262 ~ 1216731,
                                       EGID == 192045347 ~ 1266623,
                                       EGID == 192045349 ~ 1265262,
                                       EGID == 192045371 ~ 1266157,
                                       EGID == 192045414 ~ 1245467,
                                       EGID == 192045417 ~ 1266442,
                                       EGID == 192045434 ~ 1199457,
                                       TRUE ~ geocode_N_address))

```

There are multiple thousands addresses that belong to street names or highway location markers.
Only addresses with complete street, plz, and city were kept. Addresses with missing house numbers are not excluded, because there exist correct addresses without any house number.

```{r}
#| warning: false

addresses <- addresses %>%
  filter(is.na(street)==FALSE & is.na(plz)==FALSE & is.na(city)==FALSE & is.na(geocode_E_address)==FALSE)

```


Identify all the characters in the street and city names.
Replace "Umlaute" with the written-out spelling and special characters with an empty string.

```{r}
#| warning: false

# street

# street_characters <- addresses %>%
#   select(street) %>%
#   unlist %>%
#   strsplit('') %>%
#   unlist() %>%
#   unique()
#   
# street_characters

replace_special_characters <- function(text){
  
  new_text = gsub('ä', 'ae', text) 
  new_text = gsub('á', 'a', new_text) 
  new_text = gsub('à', 'a', new_text) 
  new_text = gsub('â', 'a', new_text) 
  new_text = gsub('Ä', 'AE', new_text) 
  new_text = gsub('Á', 'A', new_text)
  new_text = gsub('À', 'A', new_text)
  new_text = gsub('Â', 'A', new_text)
  new_text = gsub('ë', 'e', new_text)
  new_text = gsub('é', 'e', new_text)
  new_text = gsub('è', 'e', new_text)
  new_text = gsub('ê', 'e', new_text)
  new_text = gsub('Ë', 'E', new_text)
  new_text = gsub('É', 'E', new_text)
  new_text = gsub('È', 'E', new_text)
  new_text = gsub('Ê', 'E', new_text)
  new_text = gsub('ï', 'i', new_text)
  new_text = gsub('í', 'i', new_text)
  new_text = gsub('ì', 'i', new_text)
  new_text = gsub('î', 'i', new_text)
  new_text = gsub('Ï', 'I', new_text)
  new_text = gsub('Í', 'I', new_text)
  new_text = gsub('Ì', 'I', new_text)
  new_text = gsub('Î', 'I', new_text)
  new_text = gsub('ö', 'oe', new_text)
  new_text = gsub('ó', 'o', new_text)
  new_text = gsub('ò', 'o', new_text)
  new_text = gsub('ô', 'o', new_text)
  new_text = gsub('Ö', 'OE', new_text)
  new_text = gsub('Ó', 'O', new_text)
  new_text = gsub('Ò', 'O', new_text)
  new_text = gsub('Ô', 'O', new_text)
  new_text = gsub('ü', 'ue', new_text)
  new_text = gsub('ú', 'u', new_text)
  new_text = gsub('ù', 'u', new_text)
  new_text = gsub('û', 'u', new_text)
  new_text = gsub('Ü', 'UE', new_text)
  new_text = gsub('Ú', 'U', new_text)
  new_text = gsub('Ù', 'U', new_text)
  new_text = gsub('Û', 'U', new_text)
  new_text = gsub('ç', "c", new_text)
  new_text = gsub("[.]", '', new_text)
  new_text = gsub(",", "", new_text)
  new_text = gsub(' ', '', new_text)
  new_text = gsub('-', '', new_text)
  new_text = gsub('_', '', new_text)
  new_text = gsub("'", "", new_text)
  new_text = gsub("[+]","", new_text)
  new_text = gsub("[/]","", new_text)
  new_text = gsub("[(]","", new_text)
  new_text = gsub("[)]","", new_text)
  
  return(new_text)
}

addresses_tbl <- data.table(addresses)

# Use a parallel version of the apply function in the future.apply package

plan(multisession)

# match with the custom functions
addresses_tbl[, street_without_special := future_mapply(replace_special_characters, text = street)]

# street_short

addresses_tbl[, street_short_without_special := future_mapply(replace_special_characters, text = street_short)]


# city

addresses_tbl[, city_without_special := future_mapply(replace_special_characters, text = city)]

addresses <- data.frame(addresses_tbl)

```


Set all characters to lower case.
Create a number variable, that ignores added characters after the first number (e.g., "13.a" will be "13").

```{r}
#| warning: false

addresses <- addresses %>%
  rowwise() %>%
  mutate(street_without_special = tolower(street_without_special),
         street_short_without_special = tolower(street_short_without_special),
         city_without_special = tolower(city_without_special)) %>%
  ungroup()


remove_after_non_digit <- function(text) {
  gsub("\\D.*", "", text)
}

addresses <- addresses %>%
  mutate(street_len = nchar(street_without_special),
         street_short_len = nchar(street_short_without_special),
         number_int = remove_after_non_digit(number),
         number_int = case_when(number_int == "" ~ NA,
                                            TRUE ~ number_int),
         number_int = as.integer(number_int),
         city_len = nchar(city_without_special))

head(addresses)



```


For addresses that occur multiple times, only the ones that are flagged as official addresses by the FSO are kept:

```{r}
#| warning: false

addresses <- addresses %>%
  rowwise() %>%
  mutate(address_text = paste(street_without_special, number, plz, city_without_special, collapse =" ")) %>%
  ungroup()

addresses <- addresses %>%
  group_by(address_text) %>%
  arrange(desc(official_address)) %>%
  slice(1) %>%
  ungroup() %>%
  select(-official_address, -address_text)


addresses <- tibble::rowid_to_column(addresses, "address_id")

```


# Merge Swiss-SEP to addresses

The two datasets are merged by searching for the nearest geocode of Swiss-SEP to the geocode of the address.
The EPSG (European Petroleum Survey Group) code for the Swiss coordinate system is 2056.

```{r}
#| warning: false

addresses_sf <- addresses %>%
  st_as_sf(coords = c("geocode_E_address","geocode_N_address"), remove = FALSE, crs = 2056)

swiss_sep_sf <- swiss_sep %>%
  st_as_sf(coords = c("geocode_E_sep", "geocode_N_sep"), remove = FALSE, crs = 2056)

addresses_and_swiss_sep <- st_join(addresses_sf, swiss_sep_sf, join=st_nearest_feature)

addresses_and_swiss_sep <- addresses_and_swiss_sep %>%
  mutate(distance_address_swiss_sep = sqrt((geocode_E_address - geocode_E_sep)^2 + (geocode_N_address - geocode_N_sep)^2))


```

# Illustration

Load the map of the city of Bern and plot the addresses and Swiss-SEP positions of the Längasse Quartier.

```{r}
#| warning: false
#| output: false

st_layers(here("data", "raw", "swiss-map-vector10_2022_1166_2056.gpkg", "1166", "SMV10_CHLV95LN02.gpkg"))

```


```{r}
#| warning: false

map_bern_buildings <- st_read(here("data", "raw", "swiss-map-vector10_2022_1166_2056.gpkg", "1166", "SMV10_CHLV95LN02.gpkg"), layer = "T48_DKM10_GEBAEUDE")
map_bern_streets <- st_read(here("data", "raw", "swiss-map-vector10_2022_1166_2056.gpkg", "1166", "SMV10_CHLV95LN02.gpkg"), layer = "T45_DKM10_STRASSE")

map_längasse_buildings <- st_crop(map_bern_buildings, xmin = 2599500, xmax = 2600000, ymin = 1200280, ymax = 1200760)
map_längasse_streets <- st_crop(map_bern_streets, xmin = 2599500, xmax = 2600000, ymin = 1200280, ymax = 1200760)

addresses_and_swiss_sep_längasse <- st_crop(addresses_and_swiss_sep, xmin = 2599500, xmax = 2600000, ymin = 1200280, ymax = 1200760)

addresses_längasse <- addresses_and_swiss_sep_längasse %>%
  select(geocode_E_address, geocode_N_address) %>%
  st_drop_geometry() %>%
  st_as_sf(coords = c("geocode_E_address", "geocode_N_address"), remove = FALSE, crs = 2056)

swiss_sep_längasse <- addresses_and_swiss_sep_längasse %>%
  select(geocode_E_sep, geocode_N_sep) %>%
  st_drop_geometry() %>%
  st_as_sf(coords = c("geocode_E_sep", "geocode_N_sep"), remove = FALSE, crs = 2056)

plot_längasse_addresses <- ggplot()+
  geom_sf(data=map_längasse_buildings, fill="white", default_crs = 2056)+
  geom_sf(data=map_längasse_streets)+
  geom_sf(data=addresses_längasse, size = 2, shape = 21, fill="red")

plot_längasse_addresses_swiss_sep <- plot_längasse_addresses+
  geom_sf(data=swiss_sep_längasse, size = 2, shape = 24, fill="blue")

plot_längasse_addresses

plot_längasse_addresses_swiss_sep

address_mittelstrasse_58 <- addresses_and_swiss_sep_längasse %>%
  filter(street == "Mittelstrasse" & number == "58") %>% 
  select(geocode_E_address, geocode_N_address) %>%
  st_drop_geometry() %>%
  st_as_sf(coords = c("geocode_E_address", "geocode_N_address"), remove = FALSE, crs = 2056)
  
swiss_sep_mittelstrasse_58 <- addresses_and_swiss_sep_längasse %>%
  filter(street == "Mittelstrasse" & number == "58") %>% 
  select(geocode_E_sep, geocode_N_sep) %>%
  st_drop_geometry() %>%
  st_as_sf(coords = c("geocode_E_sep", "geocode_N_sep"), remove = FALSE, crs = 2056)

plot_mittelstrasse_58_address <- ggplot()+
  geom_sf(data=map_längasse_buildings, fill="white", default_crs = 2056)+
  geom_sf(data=map_längasse_streets)+
  geom_sf(data=address_mittelstrasse_58, size = 2, shape = 21, fill="red")

plot_mittelstrasse_58_address

plot_mittelstrasse_58_address_swiss_sep <- plot_mittelstrasse_58_address+
    geom_sf(data=swiss_sep_mittelstrasse_58, size = 2, shape = 24, fill="blue")

plot_mittelstrasse_58_address_swiss_sep

plot_mittelstrasse_58_address_all_swiss_sep <- plot_mittelstrasse_58_address+
    geom_sf(data=swiss_sep_längasse, size = 2, shape = 24, fill="blue")

plot_mittelstrasse_58_address_all_swiss_sep
  

```

# Save dataset

Create integers of the Swiss-SEP and distance variables as this was described in the concept description for the SPHN RDF Schema to reduce the risk of re-identification.

```{r}

addresses_and_swiss_sep <- addresses_and_swiss_sep %>% 
  st_drop_geometry()

addresses_and_swiss_sep <- addresses_and_swiss_sep |> 
  mutate(swiss_sep_1 = as.integer(swiss_sep_1),
         swiss_sep_2 = as.integer(swiss_sep_2),
         swiss_sep_3 = as.integer(swiss_sep_3),
         distance_address_swiss_sep = as.integer(distance_address_swiss_sep))

```


Select the variables and save the dataset after selecting variables:

```{r}
#| warning: false



addresses_and_swiss_sep <- addresses_and_swiss_sep %>%
  select(address_id, street, street_without_special, street_len, street_short, street_short_without_special, street_short_len, number, number_int, plz, city, city_without_special, city_len, swiss_sep_1, swiss_sep_2, swiss_sep_3, distance_address_swiss_sep, geocode_E_address, geocode_N_address) %>%
  rename("address_id_reference" = "address_id", "street_original" = "street","street_reference" = "street_without_special", "street_len_reference" = "street_len", "street_short_original" = "street_short","street_short_reference" = "street_short_without_special", "street_short_len_reference" = "street_short_len", "number_reference" = "number", "number_int_reference" = "number_int", "plz_reference" = "plz", "city_original" = "city","city_reference" = "city_without_special", "city_len_reference" = "city_len")


write.table(addresses_and_swiss_sep, file = here("data","processed","addresses_and_swiss_sep.csv"), sep = ";", row.names = FALSE, quote = FALSE)

saveRDS(addresses_and_swiss_sep, here("data","processed","addresses_and_swiss_sep.rds"))


```

Export the dataset after deleting the Swiss-SEP variables and adding random numbers.
This dataset with random numbers is used to demonstrate the next R script: "Transforming addresses to Swiss-SEP: Standard operating procedure".

```{r}
#| warning: false

addresses_and_swiss_sep_random <- addresses_and_swiss_sep %>%
  mutate(swiss_sep_1 = sample(seq(0:100), size = 3285111, replace = TRUE),
         swiss_sep_2 = swiss_sep_1,
         swiss_sep_3 = swiss_sep_1,
         distance_address_swiss_sep = sample(seq(0:500), size = 3285111, replace = TRUE))


write.table(addresses_and_swiss_sep_random, file = here("data","processed","addresses_and_swiss_sep_random.csv"), sep = ";", row.names = FALSE, quote = FALSE)

saveRDS(addresses_and_swiss_sep_random, here("data","processed","addresses_and_swiss_sep_random.rds"))

```


